---
title: "Creating a New worcs Project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a New worcs Project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This tutorial walks you through the steps of creating a reproducible project with the `worcs` package. The learning goals are:

- [ ] Installing WORCS using the [setup tutorial](https://cjvanlissa.github.io/worcs/articles/setup.html) (to be completed before starting the tutorial);
- [ ] Checking the installation;
- [ ] Creating a new WORCS project;
- [ ] Preparing a dataset in `prepare_data.R`;
- [ ] Adding the dataset to the repository with `open_data()`;
- [ ] Adding some basic analyses
- [ ] Registering endpoints for a reproducibility check;
- [ ] Reproducing the project

# Checking the Installation

Open RStudio. Load the `worcs` package, and run the installation check:

```{r eval = FALSE}
library(worcs)
check_worcs_installation()
```

You should see all green checkmarks, optionally some "information" messages.
If you see any failed tests - instructions should be printed on how to remedy the issue.
Please follow these instructions.
If you are in a "worcshop" with a live instructor, ask for help after you've tried to remedy the issues.

# Creating a New `worcs` Project

In Rstudio, click `File > New Project > New directory > WORCS Project Template`

Type an appropriate name for the remote Repository in its textbox.
This name will be used to create a new GitHub repository on your account.
For example, you could name it "demo_worcs_project".

Keep the checkbox for `renv` checked if you want to use dependency management (recommended).

For this tutorial - select "none" in the preregistration template dropdown menu. You can always add a preregistration later using `add_preregistration()`.

For this tutorial, select the manuscript template "github_document", which has few dependencies. Optionally, you can choose a different template.

Select a license for your project (we recommend a CC-BY license, which allows free use of the licensed material as long as the creator is credited).

When you click "Create Project", the new project should open in RStudio (either in a new, or in the current session.

Verify that you see a `README.md` file, which is the welcoming page for users of your repository.
Edit this template to explain how users should interact with the project.


# Prepare a dataset using `prepare_data.R`

The data preparation script should turn your source data into an analysis-ready `data.frame` (or other data object, but you will need to specify custom functions for reading and loading the data in that case).

Two important steps usually occur before data is added to a repository:

* Removing **any and all potentially identifying information** in the case of sensitive data
* Minimal data cleaning required to store the data to a file. The remainder of the data cleaning will be done reproducibly.

You can use your own data. If you don't have your own data, you can use some demo data:

* Allison Horst's Penguin data, available in different file types at <https://cjvanlissa.github.io/worcshop/>
* [Data on the effect of different methods of drying the hands on hang time in rock climbing](https://github.com/cjvanlissa/demo_metarep/blob/1366250e87b9b3efd164e1f6d2a1d5e6158c0602/df.csv).

Below is a minimal `prepare_data.R` script. Adapt it for your own data (which will require you to copy the file to your `worcs` project directory, and load them into memory).

```{r eval = FALSE}
# Inside prepare_data.R:
library(worcs)

# Example methods of loading a data file
# df <- readxl::read_xlsx("penguins.xlsx", 1)
# df <- foreign::read.spss("penguins.sav", to.data.frame = TRUE)
# df <- read.csv("penguins.csv", stringsAsFactors = FALSE)

# Example data
df <- iris
# Remove a colum containing "potentially identifying information"
df[["Species"]] <- NULL

# Inspect the prepared data
descriptives(df)
```


# Add the Dataset to the Repository

End the file `prepare_data.R` with the following command to save the prepared dataset and publish it on GitHub.
If you do not want to publish your data on GitHub, use `closed_data()` instead.
This tutorial assumes you use `open_data()`.

```{r eval = FALSE}
open_data(df)
```

To confirm that the project now knows how to load the dataset, remove `df` from the environment, then run `load_data()` in the console:

```{r eval = FALSE}
rm(df)
load_data()
```


# Add some demo analyses

Open your `manuscript.Rmd` file. There, edit an existing code chunk, or remove them and create a new code chunk.
First, load `worcs` and the data we just created:

```{r eval = FALSE}
# Inside manuscript.Rmd:
library(worcs)
load_data()
```

Now, add some mock analyses.

You can insert your own analysis code, or play around with the following functions:

```{r eval = FALSE}
# Descriptive statistics
res_desc <- descriptives(df)
write.csv(res_desc, "res_desc.csv", row.names = FALSE)

# Simple model
mod <- lm(Sepal.Length ~ Sepal.Width, data = df)
res_mod <- summary(mod)
write.csv(res_mod$coefficients, "res_coef.csv", row.names = FALSE)
```

Note that, in this code, we write the results to spreadsheet files.
You can also print them in the document, for example using:

```{r eval = FALSE}
knitr::kable(res_mod, caption = "My regression model coefficients, for a model with $R^2 `r report(res_mod[['r.squared']])`$.")
```

# Reproduce the Project

Run the following code in the terminal:

```{r eval = FALSE}
reproduce()
```

This should render the manuscript that you've prepared.
