---
title: "Using Endpoints to Check Reproducibility"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Endpoints to Check Reproducibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(worcs)
```

This vignette describe the `worcs` package's functionality for automating reproducibility.
The basic idea is that the entry point, endpoint (or endpoints), and recipe by which to get to the endpoint from the entry point are all well-defined.

In a typical `worcs` project, the entry point will be a dynamic document (e.g., `manuscript.Rmd`), and the endpoint will be the rendered manuscript (e.g., `manuscript.pdf`). The recipe by which to get from the entry point to the endpoint is a simple call to `rmarkdown::render("manuscript.Rmd")`.

By default, the entry point is documented in the `.worcs` project file when the project is created.

## Adding endpoints

Users can add endpoints using the function `add_endpoint("filename")`. When running this function, `filename` is added to the `.worcs` project file, and its checksum is computed so that any changes to the contents of the file can be detected.


It is also possible to specify multiple endpoints. For example, maybe the user has finalized the analyses, and wants to track reproducibility for the analysis results - but still wants to make changes to the text of the manuscript without breaking reproducibility checks.
In this case, it is useful to track files that contain analysis results instead of the rendered manuscript. Imagine these are intermediary files with analysis results:

* `descriptives.csv`: A file with the descriptive statistics of study variables
* `model_fit.csv`: A table with model fit indices for several models
* `finalmodel.RData`: An RData file with the results of the final model

These three files could be tracked as endpoints by calling `add_endpoint("descriptives.csv"); add_endpoint("model_fit.csv"); add_endpoint("finalmodel.RData")`.

## Checking reproducibility

Users can verify that the endpoint remains unchanged by calling the function `check_endpoints()`. If any endpoint has changed relative to the version stored in the `.worcs` project file, this will result in a warning message.

## Updating endpoints

To update the endpoints in the `.worcs` file, call `snapshot_endpoints()`. Always call this function to log changes to the code that should result in a different end result.

## Automating endpoint checks

If a project is connected to a remote repository on GitHub, it is possible to use GitHub actions to automatically check a project's reproducibility and signal the result of this reproducibility check by displaying a badge on the project's readme page (which is the welcome page visitors of the GitHub repository first see).

To do so, follow these steps:

1. Add endpoint using add_endpoint(); for example, if the endpoint of your analyses is a file called `'manuscript/manuscript.md'`, then you would call `add_endpoint('manuscript/manuscript.md')`
1. Run `github_action_check_endpoints()`
1. You should see a message asking you to copy-paste code for a status badge to your `readme.md`. If you do not see this message, add the following code to your readme.md manually:
    + `[![worcs_endpoints](https://github.com/YOUR_ACCOUNT/PROJECT_REPOSITORY/actions/workflows/worcs_endpoints.yaml/badge.svg)](https://github.com/YOUR_ACCOUNT/PROJECT_REPOSITORY/actions/workflows/worcs_endpoints.yaml)`
1. Commit these changes to GitHub using `git_update()`

Visit your project page on GitHub and select the `Actions` tab to see that your reproducibility check is running; visit the main project page to see the new badge in your readme.md file.
