---
title: "Setting up your computer for WORCS - Docker-edition"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting up your computer for WORCS - Docker-edition}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

If you do not want to install R, RStudio, Latex and Git on a personal computer (as described in [`vignette("setup", package = "worcs")`](https://cjvanlissa.github.io/worcs/articles/setup.html)), but would like to use Docker instead, follow these steps in order:

1. Install [Docker](https://docs.docker.com/get-docker/)
2. Open a terminal/cmd/shell.
2. Start the `worcs` image:

```{bash, eval=FALSE}
docker run -e PASSWORD=secret -p 8787:8787 -it cjvanlissa/worcs:latest
```

3. Open the address `127.0.0.1:8787/` in a browser. Login using username=rstudio and password=secret.

Then setup the container.

```{r, eval=FALSE}
renv::consent(provided = TRUE)
worcs::git_user("your_name", "your_email")
```

To terminate the container, press Ctrl + C in the terminal. To save files from a Docker session on your disk, you have to link a directory explicitly when starting the container. 

On Unix file systems, this is done as follows:

```{bash, eval=FALSE}
-v /path/on/your/pc:/home/rstudio
```

And on Windows file systems, as follows:

```{bash, eval=FALSE}
-v //c/path/on/your/windows/pc:/home/rstudio
```

Then start the Docker session using this command:

```{bash, eval=FALSE}
docker run -e PASSWORD=secret -p 8787:8787 -v /path/on/your/pc:/home/rstudio -it cjvanlissa/worcs:latest
```

That's it!
