---
title: "Setting up your computer for WORCS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{setup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(worcs)
```

Before you can use the WORCS workflow and the full functionality of the `worcs` package, you have to install several software packages, and register on GitHub. You only have to perform these steps once, and the entire process should take approximately 1 hour if you start from scratch. In case some software is already installed on your system, you can skip related steps. Follow these steps in order:

1. Install R from https://CRAN.R-project.org
2. Install 'RStudio' Desktop (Free) from [rstudio.com](https://rstudio.com/products/rstudio/download/#download)
3. Install Git from [git-scm.com](https://git-scm.com/downloads). Use the default, recommended settings. It is especially important to leave these settings selected:
    + Git from the command line and also from third party software  
    <!--*The `worcs` R-package calls Git from the command line*-->
    + Use the 'OpenSSL' library  
    <!--*For secure data transfer with GitHub*-->
    + Checkout Windows-style, commit Unix-style line endings  
    <!--*This is the preferred setting when collaborating with others on different platforms. Be prepared that, on windows, you will receive harmless notifications about LF to CRLF line endings.  *-->
    + Enable Git Credential Manager  
    <!--*For logging in to GitHub*-->
    + If you run into any trouble, a more comprehensive tutorial on installing Git is available at [happygitwithr.com](https://happygitwithr.com/install-git.html).
4. Register on 'GitHub' (alternatively: see [this vignette]() on how to use 'GitLab' or 'Bitbucket')
    + Go to [github.com](https://github.com/) and click *Sign up*. Choose an "Individual", "Free" plan.
    + Request a [free academic upgrade](https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount). This allows you to create *private repositories*, which are only visible to you and selected collaborators, and can be made public when your work is published.
5. Connect 'RStudio' to Git and GitHub (for more support, see [this 'RStudio' article](https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN), and [this blog post](https://www.r-bloggers.com/rstudio-and-github/))
    a. Open 'RStudio', open the Tools menu, click *Global Options*, and click *Git/SVN*
    b. Verify that *Enable version control interface for RStudio projects* is selected
    c. Verify that *Git executable:* shows the location of git.exe. If it is missing, manually fix the location of the file.
    d. Click *Create RSA Key*. Do not enter a passphrase. Press *Create*. A window with some information will open, which you can close.
    e. Click *View public key*, and copy the entire text to the clipboard.
    f. Close 'RStudio' (it might offer to restart by itself; this is fine)
    g. Go to [github.com](https://github.com/)
    h. Click your user icon, click *Settings*, and then select the *SSH and GPG keys* tab.
    i. Click *New SSH key*. Give it an arbitrary name (e.g., your computer ID), and paste the public key from your clipboard into the box labeled *Key*.
    j. Open 'RStudio' again (unless it restarted by itself)
6. Install all packages required for WORCS by running the following code in the 'RStudio' console. Be prepared for three contingencies:  
    + If you receive any error saying *There is no package called [package name]*, then run the code `install.packages("package name")`  
    + If you are prompted to update packages, just press [ENTER] to avoid updating packages. Updating packages this way in an interactive session sometimes leads to errors if the packages are loaded.  
    + If you see a pop-up dialog asking *Do you want to install from sources the package which needs compilation?*, click *No*.

<!-- 
k. In the 'RStudio' Console window, run the following code:```{r, eval = FALSE, echo = TRUE} system('git config --global user.email "your@email.com"') system('git config --global user.name "yourname"')

RENV WORDT NU NIET GEINSTALLEERD; TOEVOEGEN AAN SUGGESTS? 
BOVENDIEN GAAT RENV NU INITIALISEREN WANNEER JE VOOR HET EERST EEN PROJECT MAAKT. NIET HANDIG. OF MISSCHIEN WEL? 

ADD library(worcs) TO MANUSCRIPT.RMD TO HAVE RENV TRACK IT
-->

```{r installpackages, eval = FALSE, echo = TRUE}
install.packages("worcs", dependencies = TRUE)
remotes::install_github("crsh/papaja", dependencies = TRUE, update = "never")
tinytex::install_tinytex()
worcs::git_user("your_name", "your_email")
```
<!-- 
renv::consent(provided = TRUE)
Please quit and reopen your R session and IDE (if you are using one, such as RStudio or Emacs) and check if tinytex:::is_tinytex() is TRUE.-->
That's it! Everything should be installed and connected now.
