---
title: "Using Custom Synthetic Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Synthetic Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# curdir <- getwd()
thedir <- getwd()

library(worcs)
#ir.create(getwd())
file.create(file.path(thedir, ".worcs"))
#setwd(thedir)
```

```{r setup}
library(worcs)
```

Oftentimes, it is not possible to share original research data publicly, for example, due to privacy constraints.
As explained in the `worcs` paper, in such cases, it is advantageous to share a synthetic dataset instead, so that the code can still be vetted, debugged, and adapted by others.
By default, the function `closed_data()` generates a synthetic dataset using the function `synthetic()`; a rudimentary random forest-based algorithm.
However, sometimes this default option falls short.
In such cases, it is possible to fully customize synthetic dataset generation.
This vignette discusses some of the options.

## Generating Data from a Structural Equation Model

Structural equation models may have problems converging when estimated on synthetic datasets.
To avoid this problem, synthetic data can be generated directly from the SEM model.
Generating data from an SEM model will often result in a synthetic dataset that will closely reproduce the model parameters estimated on the original dataset.

### Illustrating the Problem

For this example, we will use the `PoliticalDemocracy` data included with the `lavaan` package.
Imagine that we collected these data, and are not allowed to share them.
In an existing `worcs` project, we could then store them using the command:

```{r echo = TRUE, eval = FALSE}
library(lavaan)
library(tidySEM)
set.seed(4)
dat <- PoliticalDemocracy
closed_data(dat)
```
```{r echo = FALSE, eval = TRUE, error=FALSE, warning=FALSE, message=FALSE, results = "hide"}
library(lavaan)
library(tidySEM)
dat <- PoliticalDemocracy
file.create(".worcs")
set.seed(4)
closed_data(dat, worcs_directory = thedir)
```

Now, we estimate our SEM-model, based on the example in the `lavaan` documentation:

```{r echo = TRUE, eval = FALSE}
load_data()
model <- '
ind60 =~ x1 + x2 + x3
dem60 =~ y1 + a*y2 + b*y3 + c*y4
dem65 =~ y5 + a*y6 + b*y7 + c*y8

# regressions
dem60 ~ ind60
dem65 ~ ind60 + dem60

# residual correlations
y1 ~~ y5
y2 ~~ y4 + y6
y3 ~~ y7
y4 ~~ y8
y6 ~~ y8'

fit <- lavaan::sem(model, data = dat)
tidySEM::table_results(fit)
```
```{r echo = FALSE, eval = TRUE, error=FALSE, warning=FALSE}
load_data(worcs_directory = thedir)
model <- '
ind60 =~ x1 + x2 + x3
dem60 =~ y1 + a*y2 + b*y3 + c*y4
dem65 =~ y5 + a*y6 + b*y7 + c*y8

# regressions
dem60 ~ ind60
dem65 ~ ind60 + dem60

# residual correlations
y1 ~~ y5
y2 ~~ y4 + y6
y3 ~~ y7
y4 ~~ y8
y6 ~~ y8'

fit <- lavaan::sem(model, data = dat)
tidySEM::table_results(fit)
```

This should work fine.
But what if someone tries to reproduce our analysis?
They would not have access to the original data, only the synthetic dataset.
To simulate their experience reproducing the analysis,
we can load the synthetic dataset and try to run our model:

```{r echo = TRUE, eval = FALSE}
dat2 <- read.csv("synthetic_dat.csv", stringsAsFactors = FALSE)
fit2 <- lavaan::sem(model, data = dat2)
```
```{r echo = FALSE, eval = TRUE, error=FALSE, warning=TRUE}
dat2 <- read.csv("synthetic_dat.csv", stringsAsFactors = FALSE)
fit2 <- lavaan::sem(model, data = dat2)
```

This should result in several warnings, about negative latent variable variances (an impossibility) and a warning that the observed covariance matrix of the residuals is not positive definite.
In other words: the model cannot be fit to the synthetic data,
because the structure in the data is not adequately reproduced by the default algorithm of `synthetic()`.

### Adding a Custom Dataset

A dataset generated *from the model* will be much better able to reproduce that model.
So, let's use this SEM model to generate a synthetic dataset:

```{r eval = TRUE, echo = TRUE}
set.seed(33)
dat_synthetic <- lavaan::simulateData(model = lavaan::partable(fit))
```

Note that the function `simulateData()` accepts a parameter table as its argument,
which must first be extracted from the fitted model object using `partable()`.

To add this custom synthetic dataset to our original dataset, use the function below.
Note that `original_name` should reference the *file name* of the data the synthetic dataset should be associated with, not the name of the R-object.
We started with an R-object called `dat`, which we saved to a file called `dat.csv` using the function `closed_data()`.

```{r echo = TRUE, eval = FALSE}
add_synthetic(dat_synthetic, original_name = "dat.csv")
```
```{r echo = FALSE, eval = TRUE, error=FALSE, warning=FALSE}
add_synthetic(dat_synthetic, original_name = "dat.csv", worcs_directory = thedir)
```

If we now remove the original data, and call `load_data()` again, we can verify that the synthetic dataset is loaded, and we can see that it's possible to reproduce the analysis - if not the exact results - with it:

```{r echo = TRUE, eval = FALSE}
file.remove("dat.csv")
load_data()
fit2 <- lavaan::sem(model, data = dat)
tidySEM::table_results(fit2)
```
```{r echo = FALSE, eval = TRUE, error=FALSE, warning=FALSE}
file.remove(file.path(thedir, "dat.csv"))
load_data(worcs_directory = thedir)
fit2 <- lavaan::sem(model, data = dat)
tidySEM::table_results(fit2)
```

```{r echo = FALSE, results='hide'}
f <- list.files(pattern = "_dat\\.")
file.remove(f)
file.remove(".worcs")
#setwd(curdir)
#unlink(thedir, recursive = TRUE)
```
